Title Goes Here

### 2017-08-16 analysis/paper/paper.Rmd
starting email survey analysis

```{r, setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/"
)

library(datacitation)

theme_new <- function(base_size = 12){
  theme_bw(base_size = base_size) %+replace%
    theme(
      #axis.title.x=element_blank(),
      # axis.title.y=element_blank(),
      axis.title = element_text(size = 14),
      legend.key=element_rect(colour=NA, fill =NA),
      # panel.grid = element_blank(),   
      panel.border = element_rect(fill = NA, colour = "black", size=0.5),
      panel.background = element_rect(fill = "white", colour = "black"), 
      strip.background = element_rect(fill = NA)
    )
}
```

# Introduction

Here is a citation [@Marwick2017]

@@

>>>>

```{r, setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  eval = FALSE,
  comment = "#>",
  fig.path = "../figures/"
)

library(datacitation)
```

# Email survey

```{r eval = TRUE}
library(tidyverse)
email_survey <- readr::read_csv("../data/raw_data/email_survey.csv")

# overall rate of response
emails_out <- sum(!is.na(email_survey$`email sent date`))
emails_back <- sum(!is.na(email_survey$`response received date`))
email_response_rate <- round(emails_back / emails_out, 1) * 100
data_items_received <-  sum(!is.na(email_survey$`content recieved date`))
```

Our sample focused on _Journal of Archaeological Science_ articles on experiments with stone artefacts that were published during `r min(email_survey$'publication year', na.rm = TRUE)` and `r max(email_survey$'publication year', na.rm = TRUE)`. We focused on stone artefact experiments because the all research materials are generated by the researcher so there are not other stakeholders to consider what determining how to share the data. There are also no risks of damage to people or property in sharing these data because they do not include archaeological sites or human subjects. We requested the datasets for use

We sent out `r emails_out` emails to authors of these papers, and received `r emails_back`, a `r email_response_rate`% response rate. We revieced

@@

theme_new <- function(base_size = 12){
  theme_bw(base_size = base_size) %+replace%
    theme(
      #axis.title.x=element_blank(),
      # axis.title.y=element_blank(),
      axis.title = element_text(size = 14),
      legend.key=element_rect(colour=NA, fill =NA),
      # panel.grid = element_blank(),   
      panel.border = element_rect(fill = NA, colour = "black", size=0.5),
      panel.background = element_rect(fill = "white", colour = "black"), 
      strip.background = element_rect(fill = NA)
    )
}
